\documentclass[12pt]{article}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{minted}
\usepackage{enumerate}
\usepackage{fancyvrb}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage{hyperref}
\usepackage{placeins}
\usepackage{tikz}
\usepackage{tikzsymbols}
\usepackage[most]{tcolorbox}
\usepackage{enumitem}
\usepackage{algpseudocode,algorithm,algorithmicx}
\newcommand*\DNA{\textsc{dna}}
\usetikzlibrary{positioning,calc}
\usepackage{graphicx}
\usepackage{amsmath}
%-------------------------------------------------------------------------------
% Custom commands
\usepackage{xcolor} %hilight
\newcommand{\hilight}[1]{\colorbox{yellow}{#1}}
%-------------------------------------------------------------------------------

\newtcolorbox[]{solution}[1][]{%
    breakable,
    enhanced,
    colback=white,
    title=Solution,
    #1
}


\begin{document}
\begin{center}
  \centerline{\textsc{\LARGE  Homework 3}}
  \vspace{1em}
  \textsc{\large CMU 16-782 : Planning and Decision Making in Robotics} \\
\end{center}

\section{Compilation Instructions}
Compile using : g++ planner.cpp in terminal \\
Run using : ./a.out filename.txt \\
Replace filename.txt with : 
\begin{enumerate}
    \item \textbf{Blocks world} : example.txt
    \item \textbf{Triangles and Blocks world} : example$\_$triangle.txt
    \item \textbf{Fire Extinguisher world} : example$\_$fire.txt
\end{enumerate}

\section{General Instructions}
Following are the different heuristics cases which I tried:
\begin{enumerate}
    \item \textbf{No heuristic} : Simple A-star search with no heuristic.
    \item \textbf{In admissible heuristic} : Counts the difference in number of true conditions between current state and the goal state.
    \item \textbf{Admissible heuristic} : Does another A-star search from each newly discovered state. This A-star search does not consider negative effects of the actions. The heuristic assigned in such a case is the number of steps required to reach goal state with the mentioned A-star search.
\end{enumerate}
 

\newpage
\section{Blocks Environment}
\subsection{Explanation of Environment}
\begin{enumerate}
    \item \textbf{Symbols} : A, B, C, Table
    
    \item \textbf{Conditions}:
    \begin{enumerate}
        \item On(x,y) : Block x is on y.
        \item Block(x) : x is a block.
        \item Clear(x) : x has no block on top of it.
    \end{enumerate}
    
    \item \textbf{Actions}:
    \begin{enumerate}
        \item MoveToTable(b,x) : Move block b which is on block x to table.
        \item Move(b,x,y) : Move block b from block x to block y.
    \end{enumerate}
\end{enumerate}

\subsection{Performance}
\begin{center}
\begin{tabular}{| c | c | c |}
\hline
  & \textbf{Number of Expansions} & \textbf{Time Taken(in seconds)} \\ 
 \hline
 \textbf{No heuristic} & 13 & 1 \\  
 \hline
 \textbf{Inadmissible Heuristic} & 16 & 1 \\   
 \hline
 \textbf{Admissible Heuristic} & 4 & 1 \\
\hline
\end{tabular}
\end{center}

\newpage
\section{Triangles and Blocks Environment}
\subsection{Explanation of Environment}
\begin{enumerate}
    \item \textbf{Symbols} : B0, B1, B2, B3, B4, T0, T1, Table
    
    \item \textbf{Conditions}:
    \begin{enumerate}
        \item On(x,y) : x is on y.
        \item Block(x) : x is a block.
        \item Clear(x) : x has no block/triangle on top of it.
        \item Triangle(x) : x is a triangle.
        \item NotTable(x) : x is not a table.
        
    \end{enumerate}
    
    \item \textbf{Actions}:
    \begin{enumerate}
        \item MoveToTable(b,x) : Move block/triangle b which is on block x to table.
        \item Move(b,x,y) : Move block/triangle b from block x to block y.
    \end{enumerate}
\end{enumerate}

\subsection{Performance}
\begin{center}
\begin{tabular}{| c | c | c |}
\hline
  & \textbf{Number of Expansions} & \textbf{Time Taken(in seconds)} \\ 
 \hline
 \textbf{No heuristic} & 648 & 8 \\  
 \hline
 \textbf{Inadmissible Heuristic} & 297 & 3 \\   
 \hline
 \textbf{Admissible Heuristic} & 24 & 874 \\
\hline
\end{tabular}
\end{center}

\newpage
\section{Fire Extinguisher Environment}
\subsection{Explanation of Environment}
\begin{enumerate}
    \item \textbf{Symbols} : A, B, C, D, E, F, W, Q
    
    \item \textbf{Conditions}:
    \begin{enumerate}
        \item Atrobot(x) : Robot is at x.
        \item Atquad(x) : Quadcopter is at x.
        \item Isflying(x) : x is flying.
        \item Uav(x) : x is a Quadcopter.
        \item Hascharge(x) : Quadcopter has charge.
        \item Batterylow(x) : Quadcopter has low battery.
        \item Haswater(x) : Quadcopter has water.
        \item Firealpha(x) : Fire in the initial stage.
        \item Firebeta(x) : Fire after being extinguished once.
        \item Firegamma(x) : Fire after being extinguished twice.
        \item Firedelta(x) : Fire after being extinguished thrice.
        \item Loc(x) : x is a location.
    \end{enumerate}
    
    \item \textbf{Actions}:
    \begin{enumerate}
        \item Land(b,c) : Land quadcopter on robot at location c.
        \item Fly(b) : Fly quadcopter.
        \item Charge(b) : Charge quadcopter.
        \item Move(n,m) : Move the robot from location m to location n.
        \item Movewithquad(n,m) : Move the robot with the quadcopter from location m to location n.
        \item Fillwater(b) : Fill quadcopter with water.
        \item Extinguishalpha(b) : First round of extinguishing.
        \item Extinguishbeta(b) : Second round of extinguishing.
        \item Extinguishgamma(b) : Third round of extinguishing.
    \end{enumerate}
\end{enumerate}

\subsection{Performance}
\begin{center}
\begin{tabular}{| c | c | c |}
\hline
  & \textbf{Number of Expansions} & \textbf{Time Taken(in seconds)} \\ 
 \hline
 \textbf{No heuristic} & 773 & 3 \\  
 \hline
 \textbf{Inadmissible Heuristic} & 777 & 3 \\   
 \hline
 \textbf{Admissible Heuristic} & 552 & 1143 \\
\hline
\end{tabular}
\end{center}


\end{document}